### 2018-11-14 sections/systematic_uncertainties.tex
Partly implemented D. Stoker's CDS comments

Efficiencies to tag jets from $b$- and $c$-quarks in the simulation are corrected to match the efficiencies in data by $\pt$-dependent factors,
whereas the light-jet efficiency is scaled by $\pt$- and $\eta$-dependent factors.
The $b$-jet efficiency is measured in a data sample enriched in $\ttbar$ events~\cite{Aaboud:2018xwy}, while the $c$-jet efficiency is measured
using $\ttbar$ events~\cite{ATLAS-CONF-2018-001} or $W$+$c$-jet events~\cite{Aad:2015ydr}. 
The light-jet efficiency is measured in a multijet data sample enriched in light-flavour jets~\cite{ATLAS-CONF-2018-006}.
Since the $\ttbar$ sample used to measure the $c$-jet tagging efficiency overlaps with the analysis sample, the $\Hbb$ search uses
instead the $W$+$c$-jet scale factors.  
In the case of the $\Hbb$ ($\Htautau$) search, the uncertainties on these scale factors include a total of six independent sources affecting $b$-jets, one (three) source(s) affecting $c$-jets, and 17 sources affecting light-jets. 
These systematic uncertainties are taken as uncorrelated between $b$-jets, $c$-jets, and light-jets. 
An additional uncertainty is included due to the extrapolation of these corrections to jets 
with $\pt$ beyond the kinematic reach of the data calibration samples used ($\pt>300~\gev$ for $b$- and $c$-jets, 
and $\pt>750~\gev$ for light-jets); it is taken to be correlated among the three jet flavours. 
%This uncertainty is evaluated in the simulation by comparing the tagging efficiencies while varying e.g. the fraction 
%of tracks with shared hits in the silicon detectors or the fraction of fake tracks resulting from random combinations of hits, 
%both of which typically increase at high $\pt$ due to growing track multiplicity and density of hits within the jet. 
Finally, an uncertainty related to the application of $c$-jet scale factors to $\tau$-jets is considered,
but has a negligible impact in these analyses.

>>>>

Efficiencies to tag jets from $b$- and $c$-quarks in the simulation are corrected to match the efficiencies in data by $\pt$-dependent factors,
whereas the light-jet efficiency is scaled by $\pt$- and $\eta$-dependent factors.
The $b$-jet efficiency is measured in a data sample enriched in $\ttbar$ events~\cite{Aaboud:2018xwy}, while the $c$-jet efficiency is measured
using $\ttbar$ events~\cite{ATLAS-CONF-2018-001} or $W$+$c$-jet events~\cite{Aad:2015ydr}. 
The light-jet efficiency is measured in a multijet data sample enriched in light-flavour jets~\cite{ATLAS-CONF-2018-006}.
Since the $\ttbar$ sample used to measure the $c$-jet tagging efficiency overlaps with the analysis sample, the $\Hbb$ search uses
instead the $W$+$c$-jet scale factors.  
In the case of the $\Hbb$ ($\Htautau$) search, the uncertainties on these scale factors include 
a total of 6 independent sources affecting $b$-jets, 1 (2) source(s) affecting $c$-jets, and 17 sources affecting light-jets. 
These systematic uncertainties are taken as uncorrelated between $b$-jets, $c$-jets, and light-jets. 
An additional uncertainty is included due to the extrapolation of these corrections to jets 
with $\pt$ beyond the kinematic reach of the data calibration samples used ($\pt>300~\gev$ for $b$- and $c$-jets, 
and $\pt>750~\gev$ for light-jets); it is taken to be correlated among the three jet flavours. 
%This uncertainty is evaluated in the simulation by comparing the tagging efficiencies while varying e.g. the fraction 
%of tracks with shared hits in the silicon detectors or the fraction of fake tracks resulting from random combinations of hits, 
%both of which typically increase at high $\pt$ due to growing track multiplicity and density of hits within the jet. 
Finally, an uncertainty related to the application of $c$-jet scale factors to $\tau$-jets is considered,
but has a negligible impact in these analyses.
